%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
    {LeafMatrix LLC} % Organization
    {Cedar Grove, NJ} % Location
    {Jan. 2023 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
        \item {Collaboratively develop and maintain one of the primere housing on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Managing Member \& Chief Technology Officer} % Job title
    {Wellness Direct LLC} % Organization
    {Cedar Grove, NJ} % Location
    {Jun. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {SVP, Infrastructure Architect} % Job title
    {Bank of New York Mellon} % Organization
    {New York, NY} % Location
    {May. 2016 - PRESENT} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Sr. MX.3 Environment \& Configuration Manager} % Job title
    {Murex North America} % Organization
    {New York, NY} % Location
    {Oct. 2011 - May 2016} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Murex North America} % Organization
    {New York, NY} % Location
    {Jun. 2005 - Oct. 2011} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {L-3 Titan} % Organization
    {FAA Airforce base, Pomona, NJ} % Location
    {Jan. 2005 - Jun. 2005} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
    {Danggeun Pay Inc. (KarrotPay)} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2021 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
        \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
        \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
        \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
        \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
        \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
        \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
